A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-06-17 elsfrontmatter.tex
adding all authors

\author[iiasa,nies]{Shinichiro Fujimori}
\author[iiasa]{Keywan Riahi}

\address[iiasa]{International Institute for Applied Systems Analysis,
  Schlossplatz 1, A-2361 Laxenburg, Austria}
\address[nies]{National Institute for Environmental Studies, Tsukuba, Japan}

>>>>

\author[pbl]{Maarten van den Berg}
\author[nies]{Shinichiro Fujimori}
\author[pik]{David Klein}
\author[iiasa]{Keywan Riahi}
\author[pnnl]{Steven Smith}
\author[pbl]{Detlef van Vuuren}

\address[iiasa]{International Institute for Applied Systems Analysis,
  Schlossplatz 1, A-2361 Laxenburg, Austria}
\address[nies]{National Institute for Environmental Studies, Tsukuba, Japan}
\address[pbl]{PBL Netherlands Environmental Assessment Agency, Postbus 30314, 2500 GH The Hague, Netherlands}
\address[pik]{Potsdam Institute for Climate Impact Research, Telegraphenberg A 31, 14473 Potsdam, Germany}
\address[pnnl]{Joint Global Change Research Institute, 5825 University Research Court, Suite 3500, College Park, MD 20740}
